Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-06-10 ms.tex
referee report notes

As our stellar results are model-dependent, we caution users who intend to use these 
parameters for other works, such as exoplanet population studies. When available, 
stellar parameters inferred through other techniques such as asteroseismology or 
spectroscopy should supersede these values. 
The observed photometric parameters  then consistent with spectroscopically-derived
parameters for stars with published spectra, and consistent with typical
model-dependent uncertainties
from photometric data \citep[e.g.][]{Huber14}.
We provide full samples of our posteriors on the physical parameters for each 
star\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}.

>>>>

\change{As our stellar results are model-dependent, we caution users who intend to use these 
parameters for other works, such as exoplanet population studies. When available, 
stellar parameters inferred through other techniques such as asteroseismology or 
spectroscopy should supersede these values. 
The observed photometric parameters  then consistent with spectroscopically-derived
parameters for stars with published spectra, and consistent with typical
model-dependent uncertainties
from photometric data \citep[e.g.][]{Huber14}.
We provide full samples of our posteriors on the physical parameters for each 
star\footnote{\url{http://www.astro.princeton.edu/~tdm/k2/}}.}
